\section{Work Experience}
%
\cventry{Jul 2019~--~present}{Tech Lead}{Penta}{Milano, Italy}{}{
\begin{itemize}
  \item Leading a cross-functional team (composed by designers, backend and frontend developers and
    QA~engineers) involved in the design and development of the onboarding functionalities of the
    Penta banking solution. In this role, dealing with solarisBank and IDnow requirements and API
    for onboarding German and Italian businesses~(KYB) and persons~(KYC).
  \item Participating in the definition of the new Penta architecture submitting and commenting ADRs
    (Architecture Decision Records). And proposing new methodologies and modelling systems in order
    to introduce Domain-Driven Design to the company's teams.
\end{itemize}
}
%
\cventry{May 2019~--~Jul 2019}{Senior Software Engineer}{Penta}{Milano, Italy}{}{
\begin{itemize}
  \item Working at the development of the backend services of the Penta banking solution, designing
    and implementing new features with a customer-oriented approach. Above mentioned services used
    Node.js and code was written with both JavaScript and TypeScript.
  \item Being actively involved in the recruitment processes for both development and IT managerial
    positions.
\end{itemize}
}
%
\cventry{May 2019~--~present}{Manuscript Reviewer}{Manning Publications Co.}{}{}{
\begin{itemize}
  \item As volunteer, reading manuscript chapter drafts and providing feedbacks to authors.
\end{itemize}
}
%
\cventry{Apr 2019~--~May 2019}{Senior Software Engineer}{Beesy}{Milano, Italy}{}{
\begin{itemize}
  \item Working at the implementation/enhancement of the Beesy invoicing solution. Such solution
    consisted in a web application for freelancers that provided the core functionalities to manage
    invoices (including Italian e-invoices) and expences.
\end{itemize}
}
%
\cventry{Dec 2018~--~Apr 2019}{Lead Backend Engineer}{infinitec solutions}{Milano, Italy}{}{
\begin{itemize}
  \item Managing, partly remotely, a team of backend engineers and data scientists involved in the
    design and implementation of financial modules that constituted the infinitec solutions B2B2SME
    platform. With an API-focused approach, defining interfaces of the services to fulfil product
    and partners requirements.
	\item Together with Director of Engineering, Platform Architect and other Leads, contributing in
    making decisions about the platform and the services; dealing with architectural aspects, used
    technologies and coding standards.
  \item Being actively involved in the company recruitment process: evaluating CVs and candidates in
    live coding and technical interviews.
\end{itemize}
}
%
\cventry{Aug 2018~--~Dec 2018}{Senior Backend Developer}{infinitec solutions}{Milano, Italy}{}{
\begin{itemize}
	\item Designing/developing RESTful microservices of the infinitec solutions B2B2SME platform by
    means of Java Spark and Spring Boot frameworks. Furthermore, integrating them with third-party
    APIs for enabling open banking services. Among them, connecting the platform with Fabrick
    (Gruppo Sella) APIs for the Beesy project.
\end{itemize}
}
%
\cventry{Nov 2017~--~Aug 2018}{Senior Backend Developer}{finleap}{Milano, Italy}{}{
\begin{itemize}
	\item Contributing to the development of the infinitec solutions venture B2B2SME platform. Working
    with RESTful microservices implemented by means of Java Spark and Spring Boot frameworks and
    interfacing them with AWS products (S3, SQS) and other external partner APIs.
  \item During the development, using the following technologies and libraries: Docker, PostgreSQL,
    Spring Data, Hibernate and Flyway.
\end{itemize}
}
%
\cventry{Apr 2015~--~Nov 2017}{Software Engineer}{Par-Tec S.p.A.}{Milano, Italy}{}{
\begin{itemize}
  \item Designing and developing Java services for online trading platforms. Data persistence used
    Oracle~Database and services interfaced with it using Hibernate. Communication among services
    and with external bank's systems was guaranteed by SOAP and Hessian APIs and ActiveMQ messaging.
  \item Contributing to the design and implementation of an iOS app for stocks portfolio management.
  \item Designing and developing Enterprise JavaBeans (EJB) components with the Spring framework to
    provide insurance services. Significantly having a role in the definition of SOAP and REST APIs
     together with the customer for a further contract-first implementation approach.
	\item Maintaining and extending existing Java-based web applications mainly implemented with JSP,
    Servlets and Apache Struts framework.
  \item Dedicating to R\&D activities mostly focused on measuring Java application performances with
    JMH (Java Microbenchmark Harness) and on introducing Elasticsearch and ELK (Elasticsearch,
    Logstash, Kibana stack) to implement search engines and monitoring and log analysis systems.
\end{itemize}
}
%
\cventry{2010~--~2012}
  {Server Admin Assistant}
  {Fintel Energia Group}{Pollenza MC, Italy}
  {}{
\begin{itemize}
	\item Performing administration activities of GNU/Linux systems and common services with a focus on
    security: maintaing the configurations and updates and dealing with vulnerabilies.
\end{itemize}
}
%
\cventry{2010~--~2011}
  {Web Developer}
  {CERMIS Centro ricerche e sperimentazione per il miglioramento vegetale}
  {Tolentino MC, Italy}
  {}{
\begin{itemize}
\item Migrating the company's static website to a CMS-based solution with Joomla!: designing and
  implementing custom components, models and templates to fit the company's requirements.
\end{itemize}
}
